A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-08-28 model.tex
tiny corrections

In this section we review the basic properties of the 
single-fluid mixture using Eqs.\ref{masseq}--\ref{momeq} with 
Eq. \ref{eff_energy} in place of the dust continuity equation. Our
discussion is based on the corresponding axisymmetric linearized
equations about an axisymmetric steady state. A variable $f$ is
subject to perturbations of the form 
\begin{align}
  \delta f(r,z)\exp{\left(-\ii\sigma t\right)},
\end{align}
where $\sigma$ is the complex mode frequency. In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV.\label{int_rel}
\end{align} 
The real coefficients $A,B,C,D$ can be read off 
Eq. \ref{integral_ex}. Note that $B=C$ from dynamical equilibrium
(Eq. \ref{vshear}). We now consider various limits of
Eq. \ref{int_rel}.

@@

Eq. \ref{stability_est1}---\ref{stability_est2} are easily satisfied
in thin accretion disks where radial gradients are $O(1/r)$, 
$h_\mathrm{g},\epsilon,\ll 1$ and $
\Htilde/H_\mathrm{g}\lesssim 1$. Then the
magnitude of the second term on the left-hand-side  of either
inequality is much less than unity. Thus radially smooth, strictly
isothermal disks perfectly coupled with dust are stable against
axisymmetric perturbations.

>>>>

In this section we review the basic properties of the 
single-fluid mixture using Eqs.\ref{masseq}--\ref{momeq} with 
Eq. \ref{eff_energy} in place of the dust continuity equation. Our
discussion is based on the corresponding axisymmetric linearized
equations. A variable $f$ is
subject to Eulerian perturbations of the form 
\begin{align}
  \delta f(r,z)\exp{\left(-\ii\sigma t\right)},
\end{align}
where $\sigma$ is the complex mode frequency. In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV.\label{int_rel}
\end{align} 
The real coefficients $A,B,C,D$ can be read off 
Eq. \ref{integral_ex}. Note that $B=C$ from dynamical equilibrium
(Eq. \ref{vshear}). We now consider various limits of
Eq. \ref{int_rel}.

@@

Eq. \ref{stability_est1}---\ref{stability_est2} are easily satisfied
in thin accretion disks where radial gradients are $O(1/r)$, 
$h_\mathrm{g},\epsilon,\ll 1$ and $\Htilde/H_\mathrm{g}$ not too
large.  
Then the
magnitude of the second term on the left-hand-side  of either
inequality is much less than unity. Thus radially smooth, strictly
isothermal disks perfectly coupled with dust are stable against
axisymmetric perturbations.
